resistanceModelNotesAndy

### 2015-03-21 resistanceModelNotesAndy.Rmd
progress notes

Starting resistSimple() to be able to run single simpleScenarios.

@@

>>>>

Starting resistSimple() to be able to run single simple Scenarios.

**19/3/15** sat 10.15-2.15 4hrs

[recent popgen hack](https://github.com/NESCent/r-popgen-hackathon/wiki)
Doesn't seem that useful for this project.

Good progress :
check out e.g.
`resistSimple(P_1=0.01,P_2=0.3)`

@@

1. create setInputOneScenario to enable setting inputs for a single scenario
+ sensible defaults
+ later will allow customised scenarios e.g. setInputCurtisFig1
+ will reduce code volume and repetition in createInputMatrix
